---
title: "FndtnsR_HW1"
author: "Alexis Merritt"
date: "10/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Exercises

1.  Explain coercion rules. Create an example that demonstrates the fixed order of the coercion rules.


R will try to force an input or values to be a different type so that functions can work smoothly. I'll use coercion to force a true or false statement to become a numeric
```{r}
x <- 'coercion'

xvalue <- typeof(x)

print(xvalue)

true_false_statement <- is.character(xvalue)

xcoercion <- as.numeric(true_false_statement)

print(xcoercion)
```

2.  The following code will generate a warning. Explain why.

The below statement is attempting to convert a list of characters into a list of integers but there are no defined values for these characters to be coerced into

```{r}
as.integer(c("one", "two", "three"))
```

3.  Create a vector of a sequence of integers starting at 2, ending at 100, and increasing by 2. Assign the vector to an object called `evens`. Coerce the vector to be of type `integer`. Confirm that the vector is of type `integer`.

```{r}
evens <- seq(2, 100, by = 2)

evens_coerced <- as.integer(evens)

print(typeof(evens_coerced))
```

4.  Create a vector of random numbers with a length equal to your vector in exercise 3. Use a seed with a value of 730 before creating your vector. Assign the vector to an object called `randoms`. Confirm the type of the vector.

```{r}

print(length(evens))

set.seed(730)
random_vector <- runif(50, min=0, max=100)

print(random_vector)
```

5.  Create a vector demonstrating which values in exercise 3 are greater than `0.75`. Assign the vector to an object called `logicals`. Confirm the type of the vector.

```{r}

rand_vector_logical <- runif(50, min=0, max=100) > 0.75

print(rand_vector_logical)
```

6.  Create a data frame including the three vectors created in exercises 3 through 5. Assign it to an object following best practices for naming.

```{r}

new_dataframe <- data.frame(evens, random_vector,rand_vector_logical)

print(new_dataframe)

```

7.  Create a new object which is the sum of `evens` and `randoms` all divided by 3. Demonstrate how to calculate basic summary statistics for this new object (mean, median, minimum, maximum, standard deviation, variance).

```{r}

logical_sums <- (evens + rand_vector_logicals + random_vector)/3

print(logical_sums)

```

8.  We discussed the idea that R is a "vectorized" language. Explain this concept. Why is it important?

vectorized just means that R is based around the manipulation of lists of information. That is important for data processing as most data can be broken down to vectors and manipulated for the actual analysis.

9.  Run the `sessionInfo` function in a chunk.

```{r}
sessionInfo()
```